---
title: "PresenceNetwork"
author: "Taylor"
date: "2022-10-03"
output: html_document
---
##First analysis: Presence 

#Step 1: install and run packages 

```{r echo=FALSE, warning=FALSE, error=FALSE}
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)
library(psych)
library(psychotools)
library(tidyverse)
library(semTools)
library(semPlot)
library(haven)

knitr::opts_chunk$set(echo = TRUE)
```

#Step 2: import and define dataset
```{r}
dataset <- read_sav("1st_wave_collated.sav")
View(dataset)
myvars <- c("spatial_presence", "Ig_involvement", "Ig_realism", "PEQ", "UAQ_Identification", "UAQ_immersion", "UAQ_compensation")

netdata<-dataset[myvars]

describe(netdata)

```

#Step 3: Estimate Network
```{r}

network1 <- estimateNetwork(netdata, default="EBICglasso")

```

#Step 4: Estimate network stability by bootstrapping network

#B1 = default bootstrapping 
#B2 = case dropping bootstrapping 

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, results='FALSE'}
b1 <- bootnet(network1, boots=1000, statistics=c("strength", "expectedInfluence", "edge"))

b2 <- bootnet(network1, boots=1000, type="case", statistics=c("strength", "expectedInfluence", "edge"))


```

#Step 5: Plot the Network
```{r echo=FALSE, error=FALSE, warning=FALSE}

plot(network1, layout="spring", vsize=6, border.color="black", color=c('lightblue','orange', 'red'))

```

#Step 6: Get Centrality Indices
```{r}
Centrality1 <-centralityTable(network1)
write.csv(Centrality1)
view(Centrality1)

```



#Step 7: Get centrality stability coefficient
```{r echo=FALSE, error=FALSE, warning=FALSE}
corStability(b2)

```

#Step 8: Stability of the Network Plotting
```{r}
pdf("CentrStability1.pdf")
plot(b2)
dev.off()
```

```{r}
pdf("edges.pdf")
plot(b1, "edge", plot="difference", onlyNonZero=TRUE, order = "sample")
```

##2nd Network analysis introducing IGD as assessed by the IGD9-SF

#Repeat step 2 = import and define dataset
```{r}
dataset <- read_sav("1st_wave_collated.sav")
View(dataset)
myvars2 <- c("IGD9_SF", "spatial_presence", "Ig_involvement", "Ig_realism", "PEQ", "UAQ_Identification", "UAQ_immersion", "UAQ_compensation")

netdata2<-dataset[myvars2]

describe(netdata2)

```

#Repeat step 3 = Estimate Network
```{r}

network2 <- estimateNetwork(netdata2, default="EBICglasso")

```

#Repeat step 4 = Estimate network stability by bootstrapping network

B1 = default bootstrapping 
B2 = case dropping bootstrapping 

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, results='FALSE'}
b1b <- bootnet(network2, boots=1000, statistics=c("strength", "expectedInfluence", "edge"))

b2b <- bootnet(network2, boots=1000, type="case", statistics=c("strength", "expectedInfluence", "edge"))


```

#Repeat step 5 = Plot the Network
```{r echo=FALSE, error=FALSE, warning=FALSE}

plot(network2, layout="spring", vsize=6, border.color="black", color=c('lightblue','orange', 'red'))

```

#Repeat step 6 = Get Centrality Indices
```{r}
Centrality2 <-centralityTable(network2)
write.csv(Centrality2)
view(Centrality2)

```


#Repeat step 7 = Get centrality stability coefficient
```{r echo=FALSE, error=FALSE, warning=FALSE}
corStability(b2b)

```

#Repeat step 8 = Stability of the Network Plotting
```{r}
pdf("CentrStability1.pdf")
plot(b2)
dev.off()
```

```{r}
pdf("edges.pdf")
plot(b1, "edge", plot="difference", onlyNonZero=TRUE, order = "sample")
```
